%We consider a downlink multi-cell \ac{MIMO} \ac{IBC} using \ac{OFDM} with \acl{MU} contending for space-frequency resources in a given scheduling instant. The problem is to determine the transmit precoders by the \acp{BS} in a coordinated approach to minimize the total number of backlogged packets in the \acp{BS}. The \ac{Q-WSRM} is a conventional design objective with the number of backlogged packets reflected in the corresponding weights, \textit{i.e}, the longer the queue size, the higher the priority. In contrast, we design the precoders jointly across the space-frequency resources by minimizing the total user queue deviations. The problem is nonconvex, and, therefore, we employ \ac{SCA} to solve the problem by a sequence of convex subproblems using the first order Taylor approximation. At first, we propose a centralized \ac{JSFRA} solution using two different formulations by employing the \ac{SCA} technique, namely the sum rate formulation and the \ac{MSE} reformulation. We then introduce distributed precoder designs using primal and \ac{ADMM} for the \ac{JSFRA} solutions. Finally, we propose a practical distributed iterative precoder design based on the \ac{MSE} reformulation approach by solving the \acl{KKT} conditions with closed form expressions. Numerical results are used to compare the proposed algorithms to the existing solutions.
%
%we address the queue minimizing downlink precoder design as a joint nonconvex optimization problem over space-frequency resources. We employ \ac{SCA} technique to solve the problem by a sequence of convex subproblems using inner approximations. Initially, we discuss the centralized \acl{JSFRA} solutions based on \ac{SCA} as well as by \acl{MSE} reformulation. Then we extend the distributed precoder design for the centralized schemes using primal and \ac{ADMM} method. Finally, we discuss the distributed precoder design problem by solving the \ac{KKT} expressions to obtain the closed form solutions for the transmit and the receive precoders. Numerical results are shown to compare them.
%
We consider a downlink multi-cell \ac{MIMO} \ac{IBC} using \ac{OFDM} with \acl{MU} contending for space-frequency resources in a given scheduling instant. The problem is to design the transmit precoders efficiently to minimize the total number of backlogged packets waiting at the coordinating \acp{BS}. Conventionally, the \ac{Q-WSRM} formulation with the number of backlogged packets as the corresponding weights is used to design the precoders. However, in the proposed \ac{JSFRA} formulation, the precoders are designed jointly across the space-frequency resources for all users by minimizing the total number of backlogged packets at each transmission, thereby performing user scheduling implicitly. Since the problem is nonconvex, we solve the \ac{JSFRA} formulation iteratively by solving an approximate convex subproblem in each iteration by updating the operating point. The \ac{JSFRA} formulation is solved in two different approaches, namely by the \ac{SINR} relaxation method and by the \ac{MSE} reformulation approach. We then discuss the distributed precoder designs using primal decomposition and the \ac{ADMM} for the proposed \ac{JSFRA} solutions. Finally, we propose a practical iterative precoder design by solving the \acl{KKT} expressions for the \ac{MSE} reformulation that requires minimal information exchange for each update. Numerical results are used to compare the proposed algorithms to the existing solutions.